\Huge ACM and Climate Change

### 2018-12-11 main.tex
Added couple sentences of vision

\newcommand{\bcp}[1]{\ifdraft{\bf #1}\fi}
\newcommand{\COtwoE}{CO$_2$e}

@@

Each of these strategies will have some beneficial effect on emissions.
Each may also have downsides---for example, locating conferences near their
existing ``centers of mass'' may discourage holding them in countries like
India and China where the community is still developing, while virtual PC
meetings and remote conference attendance may reduce opportunities for
informal connections and mentoring.  Getting beyond easy, short-term
solutions will require balancing competing concerns, demanding discussion,
compromise, careful analysis of data, and creative experimentation.

>>>>

\newcommand{\bcp}[1]{\ifdraft{\bf [bcp: #1]}\fi}
\newcommand{\COtwoE}{CO$_2$e}

@@

Each of these strategies will have some beneficial effect on emissions.  Of
course, each may also have downsides---for example, locating conferences
near their existing ``centers of mass'' may discourage holding them in
countries like India and China where the community is still developing,
while virtual PC meetings and remote conference attendance may reduce
opportunities for informal connections and mentoring.  Getting beyond easy,
short-term solutions will require balancing competing concerns, demanding
discussion, compromise, careful analysis of data, and creative
experimentation.  
%
\bcp{Added remainder of paragraph.  I don't think the two sentences work
together very well, but I can't decide which to keep!}
It will also require questioning some fundamental assumptions about how
research gets done---e.g., that more and bigger conferences are better, and
that personal success is (positively) correlated with time spent in
airports.
%
And to thrive in the long term, we need to begin imagining what a
zero-carbon professional society might look like.
